Numerical simulation of bubble deformation \\ and breakup under simple linear shear flows

### 2022-12-24 Bubble-deformation.tex
n-m

Table~\ref{tab:CaRecComparison} 
lists, for representative $Ca$ values,
the corresponding critical Reynolds number, $Re_{c}$, for shear-induced 
bubble breakup for a variety of flow
conditions.  The results indicate that sufficiently large shear forces are
required for bubble breakup even for large Capillary numbers. The combined
effects of very small density and viscosity ratios 
($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
act synergistically in deformation and breakup processes.
We conducted a linear least squares best fit analysis (linear vs. 
power law vs. exponential models) of the data that we 
list in Table~\ref{tab:CaRecComparison} and have found that the following
exponential model is the best fit:
%  Re = \frac{\rho_{b}UR}{\mu_{b}}, \quad
%  Ca = \frac{\mu_{b}U}{\sigma}, \quad
\begin{eqnarray}
Re_{c}=138.3 e^{-1.41 (Ca)} \label{bestfit}
\end{eqnarray}
(\ref{bestfit}) was derived from the linear least squares best fit
of the log of $Re_{c}$:
\begin{eqnarray}
	\log(Re_{c})=4.9-1.41 (Ca)  \label{bestfitraw}
\end{eqnarray}
%% variance for X^T X c = b
%% (S/(n-m)) (X^T X)^{-1}
%% standard deviation: sqrt(2.1E-3)=.05 and sqrt(4.2E-3)=0.06
The predicted variances for the parameters 
``$4.9$'' and ``$-1.41$'' which appear in (\ref{bestfitraw}) are
$2.1E-3$ and $4.2E-3$ respectively.  In other words, even with just
four data points, we have computed a reasonable best fit curve.

@@

%% variance for X^T X c = b
%% (S/(n-m)) (X^T X)^{-1}
\begin{figure}%[h!]
  \centering
  \includegraphics[width=\textwidth]{critical_Reynolds_Number_label}
  \caption{A plot of the critical Reynolds number versus Capillary number
	for the data listed in Table \ref{tab:CaRecComparison}.  The
	linear least squares best fit for the $\log(Re_{c})$ is
	$\log(Re_{c})=4.9-1.41(Ca)$ (i.e. $Re_{c}=138.3 e^{-1.41 Ca}$)
	with a predicted variance
	for the parameters ``$4.9$'' and ``$-1.41$'' being
	$2.1E-3$ and $4.2E-3$ respectively.  Even for the
	given data that we computed, it is suggested that 
	a ``bubble break-up map''
	can be derived, in which for the conditions that
	$\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$ and $0<Ca<1$, one
	can predict whether a given $(Ca,Re)$ pair will result in shear
	induced bubble break-up or not.  
	   }
  \label{fig:CaRecFit}
\end{figure}
%

>>>>

Table~\ref{tab:CaRecComparison} 
lists, for representative $Ca$ values,
the corresponding critical Reynolds number, $Re_{c}$, for shear-induced 
bubble breakup for a variety of flow
conditions.  The results indicate that sufficiently large shear forces are
required for bubble breakup even for large Capillary numbers. The combined
effects of very small density and viscosity ratios 
($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
act synergistically in deformation and breakup processes.
We conducted a linear least squares best fit analysis (linear vs. 
power law vs. exponential models) of the data that we 
list in Table~\ref{tab:CaRecComparison} and have found that the following
exponential model is the best fit:
%  Re = \frac{\rho_{b}UR}{\mu_{b}}, \quad
%  Ca = \frac{\mu_{b}U}{\sigma}, \quad
\begin{eqnarray}
Re_{c}=138.3 e^{-1.41 (Ca)} \label{bestfit}
\end{eqnarray}
(\ref{bestfit}) was derived from the linear least squares best fit
of the log of $Re_{c}$:
\begin{eqnarray}
	\log(Re_{c})=4.9-1.41 (Ca)  \label{bestfitraw}
\end{eqnarray}
%% variance for X^T X c = b
%% (S/(n-m)) (X^T X)^{-1}
%% standard deviation: sqrt(4.2E-3)=.07 and sqrt(8.4E-3)=0.09
The predicted variances for the parameters 
``$4.9$'' and ``$-1.41$'' which appear in (\ref{bestfitraw}) are
$4.2E-3$ and $8.4E-3$ respectively.  In other words, even with just
four data points, we have computed a reasonable best fit curve.

@@

%% variance for X^T X c = b
%% (S/(n-m)) (X^T X)^{-1}
\begin{figure}%[h!]
  \centering
  \includegraphics[width=\textwidth]{critical_Reynolds_Number_label}
  \caption{A plot of the critical Reynolds number versus Capillary number
	for the data listed in Table \ref{tab:CaRecComparison}.  The
	linear least squares best fit for the $\log(Re_{c})$ is
	$\log(Re_{c})=4.9-1.41(Ca)$ (i.e. $Re_{c}=138.3 e^{-1.41 Ca}$)
	with a predicted variance
	for the parameters ``$4.9$'' and ``$-1.41$'' being
	$4.2E-3$ and $8.4E-3$ respectively.  Even for the
	given data that we computed, it is suggested that 
	a ``bubble break-up map''
	can be derived, in which for the conditions that
	$\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$ and $0<Ca<1$, one
	can predict whether a given $(Ca,Re)$ pair will result in shear
	induced bubble break-up or not.  
	   }
  \label{fig:CaRecFit}
\end{figure}
%
